---
title: 'Dashboard Like a Boss'
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    orientation: rows
    css: dashboard_source_folder/css/starlight_css.css
    theme: bootstrap
    
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}

knitr::opts_chunk$set(echo = FALSE) # always echo=FALSE for dashboards. No need to show off. you can include source code if you want
# bc you set echo to false, you don't actually need include=FALSE, message=FALSE, or warning=FALSE in the 
# chunk "preamble" (can I call it that? if it's called something else can I still call it that?) 
library(flexdashboard) # dashboards!
library(highcharter)   # for interactive plots
library(DT)            # for search/filter/downloadable tables
library(tidyverse)     # doi
options(scipen=999)    # keep scientific notation turned off
source('dashboard_source_folder/R/file_export_for_dashboards.R')

```

<div class="footer">
  <p> DCR 2019 | Malorie Hughes | maloriejhughes@gmail.com | github.com/maloriejhughes </p>
</div>
  
  
```{r,echo=F}
# pdated <script> document.write(new Date().toLocaleDateString()); </script> 
# outline:
# motivation
# anatomy of a dashboard. navigation bar != header. 
# map the anatomy to the css code
# define the basic components, and the basic attributes that can be modified.
# everything is like an object. there are 
# boarders: margin, padding  [learn diff between margin and padding]
# sizes: font-size, height/width
# position: fixed, float.....

# can css take variables? how?
# can i use javascript instead? how?
# find way to set css global custom options for:
# value boxes
# highcharter
# ggplot
# datatable
# color theme


# can use shiny runtime. make a skeleton for that and put on github
# look into navigation menu drop down
# you can bring the css into your code using a chunk:
#  ```{css}
#  ```
# same way you'd do an r chunk

# create code block looking style option
```


```{r export}


```


Slides {data-orientation="columns"}
=====================================

Column {data-height=800}
-------------------------------------

```{r,dpi=240}
knitr::include_url('Slides/DashboardingSlides.html', height="850px")
```
 

1. Basic Layout
=====================================

Row {data-height=175}
-------------------------------------


### 1-10, how cool are Value Boxes?
```{r}

valueBox(2
         )
```


### 1-10, how cool are gauges?
```{r}

gauge(9 
      , min = 0 , max = 10
      , gaugeSectors( success = c(9, 10), warning = c(7, 9), danger = c(0, 7))
      )

```

### 1-10, how cool are Value Boxes + favicon icons?
```{r}

valueBox(7
         , icon="fa-tag"
         )

```

Row {data-height=300}
-------------------------------------
### stuuuuffff

```{r}





```

### more stuuuffffff

```{r}


```








Row {data-height=300}
-------------------------------------

### great insight


```{r}

```


### so actionable
```{r}

```




Row {data-height=1000, .tabset}
-------------------------------------
### omg

```{r}

          

```

### it's taaabbbed

```{r}

          
          

```






2. Printing {data-orientation="columns"}
=====================================

Column {data-height=1000}
-------------------------------------

```{r,dpi=240}
knitr::include_url('Tutorials/Table-Print-Comparison.html', height="1000px")
```
 

3. Datasets {data-orientation="columns"}
=====================================

Column {data-height=1000}
-------------------------------------

```{r,dpi=240}
knitr::include_url('Tutorials/Including-Datasets.html', height="1000px")
```

4. Interactive Viz {data-orientation="columns"}
=====================================

Column {data-height=1000}
-------------------------------------

```{r,dpi=240}
knitr::include_url('Tutorials/Highcharter-tutorial.html', height="1000px")
```
  

 
5. Exporting
=====================================

Column {data-height=1000}
-------------------------------------

```{r,dpi=300}
knitr::include_url('Tutorials/Exporting.html', height="1000px")
```
  
