---
title: 'flexdashboard Layout with Notes'
output: 
  flexdashboard::flex_dashboard:
    logo: ../dashboard_source_folder/logos/onica_amazon_small.png
    vertical_layout: scroll
    orientation: rows
    css: ../dashboard_source_folder/css/basic_css.css
    theme: bootstrap
    
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE) # always echo=FALSE for dashboards. No need to show off. you can include source code if you want
# bc you set echo to false, you don't actually need include=FALSE, message=FALSE, or warning=FALSE in the 
# chunk "preamble" (can I call it that? if it's called something else can I still call it that?) 
library(flexdashboard) # dashboards!
library(highcharter)   # for interactive plots
library(DT)            # for search/filter/downloadable tables
library(tidyverse)     # doi
options(scipen=999)    # keep scientific notation turned off
```

<div class="footer">
  <p> DCR 2019 | Malorie Hughes | maloriejhughes@gmail.com | github.com/maloriejhughes </p>
</div>
  

1. Basic Layout
=====================================

Row {data-height=175}
-------------------------------------


### 1-10, how cool are Value Boxes?
```{r}

valueBox(2
         )
```


### 1-10, how cool are gauges?
```{r}

gauge(9 
      , min = 0 , max = 10
      , gaugeSectors( success = c(9, 10), warning = c(7, 9), danger = c(0, 7))
      )

```

### 1-10, how cool are Value Boxes + favicon icons?
```{r}

valueBox(7
         , icon="fa-tag"
         )
# find more favicons here: https://fontawesome.com/icons?d=gallery
```

Row {data-height=300}
-------------------------------------
### stuuuuffff

```{r}





```

### more stuuuffffff

```{r}


```








Row {data-height=300}
-------------------------------------

### great insight


```{r}

```


### so actionable
```{r}

```




Row {data-height=1000, .tabset}
-------------------------------------
### omg

```{r}

          

```

### it's taaabbbed

```{r}

          
          

```





  

Extras: Layout 3 {data-orientation="columns"}
=====================================
<h4> COLUMN ORIENTATION ON A SINGLE PAGE?!?! </h4>

also, notice that you can put things outside of the "boxes", like header text, images, section break, etc.

Column {data-width=300}
-------------------------------------
### READ ME
<h4> Make use of your css headers</h4>
You can do the column layout, which is particularly useful if 

+ you want an informative sidebar to help the user understand what's going on in the dashboard

+ you will be comparing two things sie by side*, such as bar plots (of fixed y-axis height)

*tabs are also useful for that purpose, especially when the changes are subtle or the x-axis spans a wide range.  

<h2> now some h2!</h2>
<h3> and what was h3?</h3>
<h1> css header "functions" are the ish</h1>

Note: *When  you use column orientation, you'll have to assign the column width so that all the columns on the page sum to 1000.*



</br>
</br>


Column {data-width=700}
-------------------------------------
### so cool 1 {data-height=300}

I made this box short.  You can control the size of entire rows, columns, or the "boxes" inside a row or column. 

But, you'll notice: in the column-orientation layout, if you put text in the box instead of a plot, the box height shrinks down to a height to accomidate the text, rather than the fixed height

### so cool 2 {data-height=700}

You can force the box to keep it's assigned height by adding an empty chunk of R code (or not empty, depends on your goal) IMMEDIATELY following the text. If you leave a blank line it won't work for reasons beyond me.
```{r}

```

### so cool 3 {data-height=700}

Forcing the box size again.
```{r}

```
